InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-23 paper.tex
Add suggestions
Co-authored-by: RaphaW <116720366+RaphaW@users.noreply.github.com>

A more recent approach is presented in \cite{zellers2020defending}. With the aim to investigate in the detection of AI generated fake news,  the authors created a model called \textbf{Grover}, which is on the hand able to generate fake news, but on the other hand also pretty reliably detects, whether a given text is generated by itself. The study also elaborates on how to deal with the issue on generated fake news. Therefore, inspired by IT security research, they advocate for the release of such models, to allow the development of effective countermeasures, like detector models.

>>>>

A more recent approach is presented in \cite{zellers2020defending}. With the aim to investigate in the detection of AI generated fake news,  the authors created a model called \textbf{Grover}, which is on the one hand able to generate fake news, but on the other hand also pretty reliably detects, whether a given text is AI-generated by itself. The study also elaborates on how to deal with the issue on generated fake news. Therefore, inspired by IT security research, they advocate for the release of such models, to allow the development of effective countermeasures, like detector models.
